\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY

### 2016-02-15 draft.tex
finish legislator section of sec:model

Vote Buyer $A$ moves first, providing a bribe offer function $a(i)$. $a(i)$ is perfectly observable to Vote Buyer $B$ when he moves second and offers bribe offer function $b(i)$. Each legislator takes these bribe offers as given and then votes for the alternative that maximizes her payoff. I assume unbribed legislators who are indifferent vote for $s$.

\subsection{Legislature}
Let us look first at the legislature. Each legislator $i$ decides whether to vote for $x$ or $s$ given her preference $i$, $a(i)$ and $b(i)$. Although legislators are ordered on the interval according to their ideal points $i$, there is acknowledged uncertainty surrounding their preferences. We take this uncertainty to vary by legislator and also potentially by issue area when we extend the model to account for multi-dimensional voting and vote-buying.

In order to keep the model tractable when introduing this uncertainty, we take the ideal point function to be linear in $i$. That is, legislator $i$'s ideal point is taken to be $\alpha -\beta i$. We model uncertainty by taking legislator $i$ to vote for $x$ if 
			  \[
				  v(i) = \alpha -\beta i + \ve_i + a(i) - b(i) > 0
				\]

@@

Given these assumptions, the probability that legislator $i$ votes against the new proposal is
	\[
					\Pr\left[v(i)\leq 0 \right] = \Pr\left[\alpha -\beta i + \ve + a(i) - b(i) \leq 0 \right] = \Pr\left[\ve \leq \beta z - \alpha - a(i) + b(i) \right] 
	\]
Assuming $\ve \sim \text{Logistic} \ (0,1)$, the probability that legislator $z$ votes ``no'' is $\frac{1}{1+e^{-\left(\beta i - \alpha - a(i) + b(i) \right)}}$.

For ease of exposition, for now take $i \in \left\{ -\frac{1}{2}, 0, \frac{1}{2} \right\}$. For ease of notation, let
				\begin{enumerate}
					\item $X = -\alpha + b(0)$ 
					\item $Y = \frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
					\item $Z = -\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)\label{page:sh}$ 
				\end{enumerate}

\begin{itemize}	
			\item Then the three probabilities are
				\begin{itemize}
					\item $\frac{1}{1+e^{-\left(- \alpha + b(0) \right)}} = \frac{1}{1+e^{-X}}$, $\frac{1}{1+e^{-\left(\frac{\beta}{2}- \alpha + b(\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Z}}$, $\frac{1}{1+e^{-\left(-\frac{\beta}{2}- \alpha + b(-\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Y}}$
					\item Whether a legislator $z$ votes ``no'' is a random variable, denote it $X(z)$, distributed Bernoulli with this probability:
						\[
							X(z) \sim \text{Bernoulli}(p(z)) \hskip.2in \text{where} \hskip.2in p(z) = \frac{1}{1+e^{-\left(\beta z - \alpha + b(z) \right)}}
						\]
				\end{itemize}
		\end{itemize}

@@

			The FOC wrt to $b\left(\frac{1}{2}\right)$ is 
				\begin{equation}
					W_B \biggl[ \left( \frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2 \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \right) \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
				\end{equation}
			Simplifying:
				\begin{equation}
					W_B \biggl[ \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
					\label{eq:logistic}
				\end{equation}
			Further math related to this equation is on Page~\pageref{eq:logistic2}.
			\item If we divide through by 2, the left side is the average minus the product
			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
		\end{itemize}
	\item Vote Buyer A
		\begin{itemize}
			\item Vote buyer A's objective function is identical in form to that of Vote buyer B (Expression~\ref{eq:objb}) 
			  \begin{multline}
			    \max_{a\left(-\frac{1}{2}\right), a\left(0\right), a\left(\frac{1}{2}\right)} 
					W_A \biggl[ \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y_A}} +
					\frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Z_A}} + \\
					\frac{1}{1+e^{-Y_A}} \frac{1}{1+e^{-Z_A}} - 2	\frac{1}{1+e^{-Z_A}} \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y_A}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} a(j)
					\label{eq:obja}
				\end{multline}
				where 
				\begin{enumerate}
					\item $X_A = \alpha - b_0(\bm{a},W_B,\al,\beta) + a_0$ 
					\item $Y_A = -\frac{\beta}{2} + \alpha - b_{-.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{-.5}$
					\item $Z_A = \frac{\beta}{2} + \alpha - b_{.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{.5}$
				\end{enumerate}
				with $\bm a = \left(a_{-.5},a_0,a_{.5} \right)$
			\item Vote Buyer A's first order condition with respect to $a_0$ is more complicated because of the dependencies on $\bm a$ (should probably double check this, but it makes sense)
			 \begin{multline}
					 \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left[1+e^{-Y}\right]^2} \frac{\partial b_{-.5}}{\partial a_0} + \\ 
					\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2}\frac{\partial b_{.5}}{\partial a_0} + \\
					\frac{2+e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left[1+e^{-X}\right]^2}\left[1 - \frac{\partial b_0}{\partial a_0} \right] = \frac{1}{W_A}
					\label{eq:focA}
				\end{multline}
		\end{itemize}
\end{enumerate}

>>>>

Vote Buyer $A$ moves first, providing a bribe offer function $a_i$. $a_i$ is perfectly observable to Vote Buyer $B$ when he moves second and offers bribe offer function $b_i$. Each legislator takes these bribe offers as given and then votes for the alternative that maximizes her payoff. I assume unbribed legislators who are indifferent vote for $s$.

\subsection{Legislature}
Let us look first at the legislature. Each legislator $i$ decides whether to vote for $x$ or $s$ given her preference $i$, $a_i$ and $b_i$. Although legislators are ordered on the interval according to their ideal points $i$, there is acknowledged uncertainty surrounding their preferences. We take this uncertainty to vary by legislator and also potentially by issue area when we extend the model to account for multi-dimensional voting and vote-buying.

In order to keep the model tractable when introduing this uncertainty, we take the ideal point function to be linear in $i$. That is, legislator $i$'s ideal point is taken to be $\alpha -\beta i$. We model uncertainty by taking legislator $i$ to vote for $x$ if 
			  \[
				  v(i) = \alpha -\beta i + \ve_i + a_i - b_i > 0
				\]

@@

Given these assumptions, the probability that legislator $i$ votes against the new proposal is
	\[
					\Pr\left[v(i)\leq 0 \right] = \Pr\left[\alpha -\beta i + \ve + a_i - b_i \leq 0 \right] = \Pr\left[\ve \leq \beta z - \alpha - a_i + b_i \right] 
	\]
Assuming $\ve \sim \text{Logistic} \ (0,1)$, the probability that legislator $z$ votes ``no'' is $\frac{1}{1+e^{-\left(\beta i - \alpha - a_i + b_i \right)}}$.	Whether a legislator $i$ votes ``no'' is a random variable, denote it $Q(i)$, distributed Bernoulli with this probability:
	\[
		Q(i) \sim \text{Bernoulli}(p(z)) \hskip.2in \text{where} \hskip.2in p(z) = \frac{1}{1+e^{-\left(\beta z - \alpha -a_i+ b_i \right)}}
	\]

For ease of exposition, for now take $i \in \left\{ -\frac{1}{2}, 0, \frac{1}{2} \right\}$. Then $Y_B = \frac{\beta}{2} - \alpha - a_{-\frac{1}{2}} + b_{-\frac{1}{2}}$, $X_B = -\alpha - a_0+ b_0$ and $Z_B = -\frac{\beta}{2} - \alpha - a_{\frac{1}{2}} + b_{\frac{1}{2}}\label{page:sh}$ represent the net ideal points in terms of $B$'s probability of winning the issue. We can then write the probability that each of the legislators, respectively, votes against the new proposal as $\frac{1}{1+e^{-Y_B}}$, $\frac{1}{1+e^{-X_B}}$ and $\frac{1}{1+e^{-Z_B}}$.

Vote Buyer $A$ must take into account that Vote Buyer $B$ will react to her choice of bribes. So the net ideal points from her point of view---that is, in terms of her winning the issue---are $X_A = \alpha - b_0(\bm{a},W_B,\al,\beta) + a_0$, $Y_A = -\frac{\beta}{2} + \alpha - b_{-.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{-.5}$, and $Z_A = \frac{\beta}{2} + \alpha - b_{.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{.5}$. We can then write the probability that each of the legislators votes for the new proposal as $\frac{1}{1+e^{-Y_A}}$, $\frac{1}{1+e^{-X_A}}$ and $\frac{1}{1+e^{-Z_A}}$.

@@

			The FOC wrt to $b\left(\frac{1}{2}\right)$ is 
				\begin{equation}
					W_B \biggl[ \left( \frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2 \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \right) \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
				\end{equation}
			Simplifying:
				\begin{equation}
					W_B \biggl[ \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
					\label{eq:logistic}
				\end{equation}
			\item If we divide through by 2, the left side is the average minus the product
			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
		\end{itemize}
	\item Vote Buyer A
		\begin{itemize}
			\item Vote buyer A's objective function is identical in form to that of Vote buyer B (Expression~\ref{eq:objb}) 
			  \begin{multline}
			    \max_{a\left(-\frac{1}{2}\right), a\left(0\right), a\left(\frac{1}{2}\right)} 
					W_A \biggl[ \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y_A}} +
					\frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Z_A}} + \\
					\frac{1}{1+e^{-Y_A}} \frac{1}{1+e^{-Z_A}} - 2	\frac{1}{1+e^{-Z_A}} \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y_A}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} a(j)
					\label{eq:obja}
				\end{multline}
				where 
				\begin{enumerate}
					\item $X_A = \alpha - b_0(\bm{a},W_B,\al,\beta) + a_0$ 
					\item $Y_A = -\frac{\beta}{2} + \alpha - b_{-.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{-.5}$
					\item $Z_A = \frac{\beta}{2} + \alpha - b_{.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{.5}$
				\end{enumerate}
				with $\bm a = \left(a_{-.5},a_0,a_{.5} \right)$
			\item Vote Buyer A's first order condition with respect to $a_0$ is more complicated because of the dependencies on $\bm a$ (should probably double check this, but it makes sense)
			 \begin{multline}
					 \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left[1+e^{-Y}\right]^2} \frac{\partial b_{-.5}}{\partial a_0} + \\ 
					\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2}\frac{\partial b_{.5}}{\partial a_0} + \\
					\frac{2+e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left[1+e^{-X}\right]^2}\left[1 - \frac{\partial b_0}{\partial a_0} \right] = \frac{1}{W_A}
					\label{eq:focA}
				\end{multline}
		\end{itemize}
\end{enumerate}
